From Freebase to Wikidata: The Great Migration

### 2015-10-05 paper.tex
Some introduction, paper structure, and bibliography fixes.

Moving data between two knowledge bases that do not share a~similar design
is usually a~problematic task and requires the careful mapping between their structures.
In this paper, we describe how we facilitated the migration of Freebase content to Wikidata.
That migration made no exception to the rule, and had a~number of structural challenges.
Even more challenging was the cultural difference between the two involved communities.
The Freebase and Wikidata communities have a~very different background,
subtly different goals and understandings of their tasks,
and different requirements regarding their data.
This paper is structured as follows.
After a~short introduction to the two databases, we describe our methodology and
the metrics used to measure the migration.
In order to support the migration, we have developed a~set of open source tools
that we present in the following.
We then present the results of the migration and discuss these numbers,
as well as proposed next steps.

\section{Background}

@@

\section{Challenges of the migration}

@@

\subsection{Data quality}

@@

\subsubsection{Mappings of items}

@@

\subsubsection{Mapping of properties}

@@

\section{How numbers lie}

@@

\section{Statistics on the migration}

@@

\section{What could we do next?}

@@

\section{Conclusion}

>>>>

Moving data between two knowledge bases that do not share a~similar design
is usually a~problematic task and requires the careful mapping between their structures.
In this paper, we describe how we facilitated the migration of Freebase content to Wikidata.
That migration was no exception to this rule, and had a~number of \emph{structural} challenges.
Even more challenging was the \emph{cultural} difference between the two involved communities.
The Freebase and Wikidata communities have a~very different background,
subtly different goals and understandings of their tasks,
and different requirements regarding their data.
\todo{Expand}

The remainder of this paper is structured as follows.
After an introduction to the two collaborative knowledge bases
Freebase and Wikidata in \autoref{sec:background},
we describe our methodology and the metrics used to measure the migration
in \autoref{sec:challenges-of-the-migration}.
In order to support the migration, we have developed a~set of open source tools
that we present in \autoref{sec:primary-sources-tool}.
We then present the results of the migration
and discuss these statistics in \autoref{sec:statistics-of-the-migration}.
The paper terminates with an outlook at proposed next steps
and a~conclusion in \autoref{sec:future-work-and-conclusion}.

\section{Background}\label{sec:background}

@@

\section{Challenges of the migration}\label{sec:challenges-of-the-migration}

@@

\subsection{Data Quality}

@@

\subsubsection{Mappings of Items}

@@

\subsubsection{Mapping of Properties}

@@

\section{Primary Sources Tool}\label{sec:primary-sources-tool}

\subsection{Data Preparation}

\todo{Denny: write me}

\subsection{Back-end of the Tool}

\todo{Sebastian: write me}

\subsection{Front-end of the Tool}

\todo{Tom: write me}

\section{Statistics on the Migration}\label{sec:statistics-of-the-migration}

@@

\subsection{Raw Statistics}

@@

\section{Future Work and Conclusion}\label{sec:future-work-and-conclusion}

@@
